Approximation as Differentiation notes

### 2025-02-25 notes/sec/fam.tex
Assume C locally small.

\begin{definition}[$\Fam(I,C)$]
For any set $I$ and any category $C$ write $\Fam(I,C)$ for the category where:
\begin{itemize}
\item objects are the $I$-indexed families of objects of $C$;
\item morphisms from $X$ to $Y$ are families of morphisms $f_i: X_i \to Y_i$ in $C$ for any $i \in I$.
\end{itemize}
\end{definition}

@@

>>>>

\begin{definition}[Category of $I$-indexed families of objects]
For any set $I$ and any category $C$ write $\Fam(I,C)$ for the category where:
\begin{itemize}
\item objects are the $I$-indexed families of objects of $C$;
\item morphisms from $X$ to $Y$ are families of morphisms $f_i: X_i \to Y_i$ in $C$ for any $i \in I$.
\end{itemize}
\end{definition}

@@

\begin{proposition}
Suppose $C$ a locally small category.
\begin{enumerate}
\item If $C$ has binary coproducts and set-indexed products, then $\Fam(C)$ is symmetric monoidal, with the
coproduct as the monoidal product.
\item If the coproducts are in fact biproducts, then $\Fam(C)$ is Cartesian closed.
\end{enumerate}
\end{proposition}

\begin{itemize}
\item The internal hom $[X, Y]$
\end{itemize}
